\section{Broader Impact, Education, and Outreach}
\label{sec:impact}

\paragraph{Broader Impact.} 
FIX ME.

We will add to the national computing infrastructure by implementing
and making available all of the component
systems we build as part of this project.  These tools will add to the national research and industry
software infrastructure. Our prior tools are in wide use in industry
and academia, and we expect these will be also.

\paragraph{Education.}
Building and experimenting with new types of data debugging techniques will create opportunities for students of all levels to become involved in research. The PIs' goal is to encourage this participation through class projects at the undergraduate and graduate levels, and through direct involvement of the students in research. The PIs commonly extract interesting sub-projects from their ongoing research and offer them as class projects in their graduate classes at the University of Massachusetts, Amherst. The PIs have also a history of involving undergraduate students in their research, many of them women and minority students. co-PI Meliou regularly involves women and undergraduate students in her research projects. She recently advised an undergraduate student at the University of Washington in the design of an interactive web interface to the Tiresias system, which won the best demonstration award at SIGMOD 2012. \todo{add Emery}



\paragraph{Outreach.}
Improving participation in computer science from underrepresented groups
requires outreach at multiple levels; the PIs have a strong track record
of this work at both the undergraduate and graduate levels.

PI Berger has supervised undergraduate research and
mentored women and minority undergraduates. PI Berger has recruited undergraduates from
across the neighboring Five College consortium (which includes Amherst
and Hampshire Colleges, and two female-only undergraduate institutions,
Smith and Mt. Holyoke Colleges).

co-PI Meliou has supervised graduate and undergraduate students in research projects. She is currently advising three students: one female graduate student and two undergraduates (one male and one female). co-PI Meliou is passionate about promoting the participation of women and minorities in science through outreach efforts and minority group leadership.

% PI Berger participated in a discipline
% CRA-W workshop for under-represented minorities in 2008.
