\section{Research Schedule} % (fold)
\label{sec:research_schedule}

\paragraph{Year 1.} % (fold)
\label{par:year_1}
During year 1, the PIs will focus on small-scale and medium-scale data
debugging, including the static analysis of spreadsheet functions and
SQL queries. We will study different functions, patterns, and query
types. We will start experimenting both with synthetic and real-world
data early to assess the performance gains of static analysis. At the
end of year 1, we will evaluate the performance trade-off between
alternative strategies.
% paragraph year_1 (end)

\paragraph{Year 2.} % (fold)
\label{par:year_2}
During year 2, the PIs will shift our focus to medium-scale and
large-scale data debugging. We will design and implement an optimizer
for impact analysis in relational data, modeled after traditional
database optimizers. Our design will be based on complexity results
and pattern-based heuristics.  As part of this work, we will
investigate query rewrites that may lead to more efficient impact
calculations. We will begin development work on infrastructure for
augmenting MapReduce pipelines, building on Hadoop.
% paragraph year_2 (end)

\paragraph{Year 3.} % (fold)
\label{par:year_3}
During year 3, the PIs will focus their efforts exclusively on
large-scale data debugging. We will build analysis tools and complete
development of our augmented MapReduce pipeline infrastructure and
integration with a FlumeJava variant (Apache Crunch). We will evaluate this
work on large-scale MapReduce workloads available publicly and within
the PIs department.

% paragraph year_3 (end)

% section research_schedule (end)
